Project 2

### 2021-10-11 project_2.Rmd
NRC implemented

```{r load_libraries}
#loading all the necessary libraries
library(gutenbergr)
library(tidytext)
library(tidyverse)
library(readtext)
library(sentimentr)
```

@@

hemingway_corpus <- bind_rows(The_Sun_Also_Rises_Hemingway_Ernest,The_Old_Man_and_the_Sea_Hemingway_Ernest,For_Whom_the_Bell_Tolls_Hemingway_Ernest,A_Farewell_to_Arms_Hemingway_Ernest)
```

```{r new_sentiment_analysis}
#temp <- hemingway_corpus %>% unnest_regex(sentences, text, pattern = "[.?!]", to_lower = TRUE)
my_text <- read_file("The Great Gatsby_Fitzgerald, F. Scott (Francis Scott)_clean.txt")
my_text <- get_sentences(my_text)
total_sentiment <- sentiment(my_text)
total <- sum(total_sentiment$sentiment)
```

@@

```{r tidy_hemingway}
#breaking up texts into words
tidy_hemingway <- hemingway_corpus %>% unnest_tokens(word, text) %>% anti_join(stop_words)
```

```{r tidy_fitzgerald}
#breaking up texts into words
tidy_fitzgerald <- fitzgerald_corpus %>% unnest_tokens(word, text) %>% anti_join(stop_words)
```

>>>>

```{r load_libraries}
#loading all the necessary libraries
library(gutenbergr)
library(tidytext)
library(tidyverse)
library(readtext)
library(sentimentr)
library(ggiraphExtra)
library(ggplot2)
library(RColorBrewer)
library(scales)
```

@@

The_Garden_of_Eden_Hemingway <- read_delim("The Garden of Eden_Hemingway_clean.txt", 
    delim = "\t", quote = "\\\"", escape_double = FALSE, 
    trim_ws = TRUE)
The_Garden_of_Eden_Hemingway_Ernest <- The_Garden_of_Eden_Hemingway %>% mutate(author = "Hemingway, Earnest", .after = text) %>% mutate(title = "The Garden of Eden", .before = author)

hemingway_corpus <- bind_rows(The_Sun_Also_Rises_Hemingway_Ernest,The_Old_Man_and_the_Sea_Hemingway_Ernest,For_Whom_the_Bell_Tolls_Hemingway_Ernest,A_Farewell_to_Arms_Hemingway_Ernest,The_Garden_of_Eden_Hemingway_Ernest)
```

```{r new_sentiment_analysis}
#temp <- hemingway_corpus %>% unnest_regex(sentences, text, pattern = "[.?!]", to_lower = TRUE)
my_text <- read_file("~/Digital.Humanities/dh_proj_2/The Garden of Eden_Hemingway_clean.txt")
my_text <- get_sentences(my_text)
new_text <- c(my_text)
total_sentiment <- sentiment(my_text)
total <- sum(total_sentiment$sentiment)
```

@@

```{r tidy_hemingway}
#breaking up texts into words
tidy_eden <- The_Garden_of_Eden_Hemingway_Ernest %>% unnest_tokens(word, text) %>% anti_join(stop_words)
tidy_hemingway <- hemingway_corpus %>% unnest_tokens(word, text) %>% anti_join(stop_words)
```

```{r tidy_fitzgerald}
#breaking up texts into words
tidy_gatsby <- The_Great_Gatsby %>% unnest_tokens(word, text) %>% anti_join(stop_words)
tidy_fitzgerald <- fitzgerald_corpus %>% unnest_tokens(word, text) %>% anti_join(stop_words)
```

```{r sentiment_nrc}
nrc_list <- get_sentiments("nrc")
counter <- tidy_hemingway %>% inner_join(nrc_list) %>% count(word, sort = TRUE)
sentiment_h <- tidy_hemingway %>% inner_join(get_sentiments("nrc") %>% 
                 filter(sentiment %in% c("anger", 
                                         "anticipation", "disgust", "fear", "joy", "sadness", "surprise", "trust"))
    ) %>%
  count(sentiment) %>%
  pivot_wider(names_from = sentiment,
              values_from = n,
              values_fill = 0) %>% mutate(author = "Hemingway")#%>% 
  #mutate(sentiment = positive - negative)
sentiment_h3 <- tidy_eden %>% inner_join(get_sentiments("nrc") %>% 
                 filter(sentiment %in% c("anger", 
                                         "anticipation", "disgust", "fear", "joy", "sadness", "surprise", "trust"))
    ) %>%
  count(sentiment) %>%
  pivot_wider(names_from = sentiment,
              values_from = n,
              values_fill = 0) %>% mutate(author = "Hemingway")
sentiment_h2 <- sentiment_h[,-9]/126688
sentiment_h2 <- sentiment_h2*100
sentiment_h2 <- sentiment_h2 %>% mutate(author = "Hemingway")
#anger	anticipation	disgust	fear	joy	sadness	surprise	trust
```

```{r}
nrc_joy <- get_sentiments("nrc")
#tidy_hemingway %>% inner_join(nrc_list) %>% count(word, sort = TRUE)
sentiment_f <- tidy_fitzgerald %>% inner_join(get_sentiments("nrc") %>% 
                 filter(sentiment %in% c("anger", 
                                         "anticipation", "disgust", "fear", "joy", "sadness", "surprise", "trust"))
    ) %>%
  count(sentiment) %>%
  pivot_wider(names_from = sentiment,
              values_from = n,
              values_fill = 0) %>% mutate(author = "Fitzgerald")
sentiment_f3 <- tidy_gatsby %>% inner_join(get_sentiments("nrc") %>% 
                 filter(sentiment %in% c("anger", 
                                         "anticipation", "disgust", "fear", "joy", "sadness", "surprise", "trust"))
    ) %>%
  count(sentiment) %>%
  pivot_wider(names_from = sentiment,
              values_from = n,
              values_fill = 0) %>% mutate(author = "Fitzgerald")
sentiment_f2 <- sentiment_f[,-9]/134829
sentiment_f2 <- sentiment_f2*100
sentiment_f2 <- sentiment_f2 %>% mutate(author = "Fitzgerald")
```

```{r}
sentiment_table <- bind_rows(sentiment_h, sentiment_f)
#sentiment_table2 <- bind_rows(sentiment_f3, sentiment_h3)
ggRadar(
  data = sentiment_table,
  mapping = aes(color = author),
  rescale = FALSE,
  interactive = TRUE,
  use.label = TRUE,
  size = 2,
  legend.position = "right"
)
```
```{r}
ggplot(data=sentiment_table, aes(x=anger, y=anticipation, fill=author)) +
  geom_bar(stat="identity")
